The SMT Competition 2015--2018

### 2018-10-23 2018/report/SMT-COMP.tex
Nicer typesetting of SMT-LIB syntax; separate file size distributions

@@

\begin{abstract}
  The International Satisfiability Modulo Theories Competition is an
  annual competition between Satisfiability Modulo Theories~(SMT)
  solvers.  The 2018 edition of the competition was part of the FLoC
  Olympic Games, which comprised 14 competitions in various areas of
  computational logic.  We report on the design and selected results
  of the SMT Competition during the last FLoC Olympiad, from 2015 to
  2018. \TODO: some notable observations/conclusions?
\end{abstract}

@@

Benchmarks in the SMT Library are written in the SMT-LIB
language~\cite{BarFT-RR-17}, a text-based format that defines the
syntax and semantics of solver input and output.  This includes a
language for terms and formulas, and a command language for
interacting with SMT solvers.  For instance,
Figure~\ref{fig:smtlib-example} shows the example formula from
Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax.
In~2016, benchmarks were updated from version~2.0 to version~2.5 of
the SMT-LIB language.  Since~2017, benchmarks are written in
version~2.6.  Fortunately, versions~2.5 and~2.6 are largely
backwards-compatible to 2.0, so that older solvers are still able to
compete with at most minor modifications.

\begin{figure}
\begin{verbatim}
(set-info :smt-lib-version 2.6)
(set-logic QF_UFLIA)
(set-info :status unsat)
(declare-fun x () Int)
(declare-fun y () Int)
(declare-fun f (Int) Int)
(declare-fun P (Int) Bool)
(assert (and (<= x y) (<= y x) (P (- (f x) (f y))) (not (P 0))))
(check-sat)
(exit)
\end{verbatim}
\caption{A benchmark problem in SMT-LIB syntax.}
\label{fig:smtlib-example}
\end{figure}

@@

    \draw [fill=black] (0.5,0) rectangle (1.5,5.1630077857); % 54535
    \draw [fill=black] (2.25,0) rectangle (3.25,5.5885514492); % 161995
    \draw [fill=black] (4,0) rectangle (5,5.3624537158); % 90841
    \draw [fill=black] (5.75,0) rectangle (6.75,4.9369959734); % 30588
    \draw [fill=black] (7.5,0) rectangle (8.5,4.4297518088); % 8355
    \draw [fill=black] (9.25,0) rectangle (10.25,3.3931037653); % 589
    \draw [fill=black] (11,0) rectangle (12,2.7264453999); % 107
    \draw [fill=black] (12.75,0) rectangle (13.75,0.9); % 1

@@

    \node [] at (7,-1) {\small File size in bytes};
  \end{tikzpicture}}
  \caption{Distribution of SMT-LIB benchmarks by file size (2018).}
  \label{fig:benchmark-sizes}
\end{figure}

@@

\begin{table}
  \caption{Wall-clock time limits}
  \label{table:time-limits}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    Main track        & 40\,min & 40\,min & 20\,min & 20\,min \\
    Application track & 40\,min & 40\,min & 40\,min & 40\,min \\
    Unsat-core track  &      -- & 40\,min & 40\,min & 40\,min \\
    \hline
  \end{tabular}
\end{table}

>>>>

\usepackage{listings}
\lstdefinelanguage{smtlib2}
  {alsoletter={-, =},
   morekeywords={set-logic,declare-fun,assert,check-sat,set-info,exit},
   sensitive=false,
   morecomment=[l]{;}}
\lstset{language=smtlib2,
basicstyle=\sffamily,
numbers=none,
keywordstyle=\bfseries\sffamily,
keywordstyle={[2]\bfseries\sffamily\underbar}
}

@@

\begin{abstract}
  The International Satisfiability Modulo Theories Competition is an
  annual competition between Satisfiability Modulo Theories~(SMT)
  solvers.  The 2018 edition of the competition was part of the FLoC
  Olympic Games, which comprised 14 competitions in various areas of
  computational logic.  We report on the design and selected results
  of the SMT Competition during the last FLoC Olympiad, from 2015 to
  2018.  These competitions set several new records regarding the
  number of participants, number of benchmarks used, and amount of
  computation performed.
\end{abstract}

@@

Benchmarks in the SMT Library are written in the SMT-LIB
language~\cite{BarFT-RR-17}, a text-based format that defines the
syntax and semantics of solver input and output.  This includes a
language for terms and formulas, and a command language for
interacting with SMT solvers.  For instance,
Figure~\ref{fig:smtlib-example} shows the example formula from
Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax, with
commands to the SMT solver typeset in bold.  In~2016, benchmarks were
updated from version~2.0 to version~2.5 of the SMT-LIB language.
Since~2017, benchmarks are written in version~2.6.  Fortunately,
versions~2.5 and~2.6 are largely backwards-compatible to 2.0, so that
older solvers are still able to compete with at most minor
modifications.

\begin{figure}
\begin{lstlisting}
(set-info :smt-lib-version 2.6)
(set-logic QF_UFLIA)
(set-info :status unsat)
(declare-fun x () Int)
(declare-fun y () Int)
(declare-fun f (Int) Int)
(declare-fun P (Int) Bool)
(assert (and (<= x y) (<= y x) (P (- (f x) (f y))) (not (P 0))))
(check-sat)
(exit)
\end{lstlisting}
\caption{A benchmark problem in SMT-LIB syntax.}
\label{fig:smtlib-example}
\end{figure}

@@

    \draw [fill=black] (0.5,0) rectangle (1,5.1629791157); % 54531
    \draw [fill=black] (2.25,0) rectangle (2.75,5.5836542368); % 159978
    \draw [fill=black] (4,0) rectangle (4.5,5.350394013); % 88081
    \draw [fill=black] (5.75,0) rectangle (6.25,4.8786283826); % 26345
    \draw [fill=black] (7.5,0) rectangle (8,4.3889077926); % 7526
    \draw [fill=black] (9.25,0) rectangle (9.75,3.1918883971); % 352
    \draw [fill=black] (11,0) rectangle (11.5,2.2422255245); % 31
    %\draw [fill=black] (12.75,0) rectangle (13.25,0); % 0

    \draw [fill=white] (1,0) rectangle (1.5,1.4418539922); % 4
    \draw [fill=white] (2.75,0) rectangle (3.25,3.8742353084); % 2017
    \draw [fill=white] (4.5,0) rectangle (5,3.9968181739); % 2760
    \draw [fill=white] (6.25,0) rectangle (6.75,4.1649057286); % 4243
    \draw [fill=white] (8,0) rectangle (8.5,3.5266990775); % 829
    \draw [fill=white] (9.75,0) rectangle (10.25,3.0372735114); % 237 
    \draw [fill=white] (11.5,0) rectangle (12,2.5927322331); % 76
    \draw [fill=white] (13.25,0) rectangle (13.75,0.9); % 1

@@

    \node [] at (7,-1) {\small File size in bytes};
  \end{tikzpicture}}
  \caption{Distribution of SMT-LIB benchmarks by file size (2018), for
    non-incremental~($\blacksquare$) and incremental~($\square$)
    benchmarks.}
  \label{fig:benchmark-sizes}
\end{figure}

@@

\begin{table}
  \caption{Wall-clock time limits}
  \label{table:time-limits}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    Main track        & 40~min & 40~min & 20~min & 20~min \\
    Application track & 40~min & 40~min & 40~min & 40~min \\
    Unsat-core track  &     -- & 40~min & 40~min & 40~min \\
    \hline
  \end{tabular}
\end{table}
